A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Progress

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  There are five contours:
the clique encoding \cite{DBLP:conf/cp/McCreeshNPS16}, CP-FC
\cite{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS
FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2000 of the 4110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3506 instances that
could be solved by at least one of \McSplit, CP-FC and clique in less than than
1000 seconds, there were only 126 instances on which \McSplit\ was not strictly
faster than the other two solvers.

\paragraph{Vertex and edge labels, directed} Cumulative run times for this
class of instances are in \cref{figure:33ved-cumulative}.  Again, \McSplit\ is
over an order of magnitude faster than the best existing CP algorithm, which is
CP-MAC in this case.  The clique encoding outperforms the other
algorithms---including \McSplit---on these labelled instances, except in the
very easy region of instances that can be solved in well under 100 ms.

\paragraph{No Vertex or edge labels, undirected, connected} are in
\cref{figure:plain-connected-cumulative}.  These results are very similar to
the corresponding experiment in which the subgraph is not required to be
connected (\cref{figure:plain-cumulative}).

\paragraph{Vertex and edge labels, undirected, connected} For the labelled,
connected case, clique slightly outperforms \McSplit\ on harder instances
(\cref{figure:33ve-connected-cumulative}).  The gap between the two algorithms
is narrow; indeed, the cumulative curve for \McSplit\ briefly rises above
the curve for clique at a runtime just below 100 seconds.

\begin{figure}[ht]
    \centering
    \subfigure[][MCS unlabelled undirected instances] {
        \centering
        \includegraphics*{gen-graph-plain-connected-cumulative.pdf}
        \label{figure:plain-connected-cumulative}
    }

>>>>

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  There are five contours:
the clique encoding \citep{DBLP:conf/cp/McCreeshNPS16}, CP-FC
\citep{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS
FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2000 of the 4110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3506 instances that
could be solved by at least one of \McSplit, CP-FC and clique in less than than
1000 seconds, there were only 126 instances on which \McSplit\ was not strictly
faster than the other two solvers.

\paragraph{Vertex and edge labels, directed} Cumulative run times for this
class of instances are in \cref{figure:33ved-cumulative}.  Again, \McSplit\ is
over an order of magnitude faster than the best existing CP algorithm, which is
CP-MAC in this case. Matching the conclusions of
\citet{DBLP:conf/cp/McCreeshNPS16}, we see that the clique encoding outperforms
the other algorithms---including \McSplit---on these labelled instances, except
in the very easy region of instances that can be solved in well under 100 ms.

\paragraph{Unlabelled, undirected, connected} This class of instances are shown
in \cref{figure:plain-connected-cumulative}.  These results are very similar to
the corresponding experiment in \cref{figure:plain-cumulative} in which the
subgraph is not required to be connected.

\paragraph{Vertex and edge labels, undirected, connected} For the labelled,
connected case, clique slightly outperforms \McSplit\ on harder instances
(\cref{figure:33ve-connected-cumulative}). However, the gap between the two algorithms
is very narrow, and is probably down to quality of implementation; indeed, the
cumulative curve for \McSplit\ briefly rises above the curve for clique at a
runtime just below 100 seconds. Additionally, \McSplit\ is the clear winner for
easier instances, where the clique encoding is relatively expensive to
construct but trivial to solve.

\begin{figure}[t]
    \centering
    \subfigure[][MCS unlabelled undirected instances] {
        \centering
        \includegraphics*{gen-graph-plain-connected-cumulative.pdf}
        \label{figure:plain-connected-cumulative}
    }
